---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oncokbR

<!-- badges: start -->
<!-- badges: end -->

{oncokbR} allows you to annotate genomic data sets using MSK's [OncoKB Precision Oncology Knowledge Base](https://www.oncokb.org/) directly in R. The package wraps existing [OncoKB API endpoints](https://api.oncokb.org/oncokb-website/api) so R users can easily leverage the existing API to annotate data on mutations, copy number alterations and fusions.


This package is compatible with oncoKB data v3.16, but is subject to change as new versions are released. For more information on oncoKB, see [Chakravarty et al. 2017](https://ascopubs.org/doi/full/10.1200/PO.17.00011). 

## Installation

You can install the development version of oncokbR like so:

``` r
remotes::install_github('karissawhiting/oncokbR')
```

## Annotate Data

### Annotate Mutations:

```{r}
library(oncokbR)
library(dplyr)
```

Annotate MAF data with tumor type indicated for annotations on oncogenicity and oncoKB treatment levels:

```{r }
blca_mutation <- oncokbR::blca_mutation %>%
  mutate(tumor_type = "BLCA")

annotated_tt <- annotate_mutations(mutations = blca_mutation[1:50,])

annotated_tt %>%
  select(oncogenic) %>% 
  table()

```


```{r}
annotated_tt %>%
  select(treatments_level ) %>% 
  table()
```

You can also annotated with no tumor type data for oncogenicity only: 

```{r }
blca_mutation <- oncokbR::blca_mutation

annotated_no_tt <- annotate_mutations(mutations = blca_mutation[1:50,])

annotated_no_tt %>%
  select(oncogenic) %>% table()
```


### Annotate CNA:

```{r}
blca_cna <- blca_cna %>%
  mutate(tumor_type = "BLCA")


annotated <- annotate_cna(blca_cna[1:10,])
table(annotated$oncogenic)

```

### Annotate Structural Variants:

```{r}

blca_sv <- blca_sv %>%
  mutate(tumor_type = "BLCA")


annotated <- annotate_sv(blca_sv[1:10,])
table(annotated$oncogenic)
```
