---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oncokbR

<!-- badges: start -->
<!-- badges: end -->

{oncokbR} allows you to annotate genomic data sets using MSK's [OncoKB Precision Oncology Knowledge Base](https://www.oncokb.org/) directly in R. The package wraps existing [OncoKB API endpoints](https://api.oncokb.org/oncokb-website/api) so R users can easily leverage the existing API to annotate data on mutations, copy number alterations and fusions.


This package is compatible with oncoKB data v3.16, but is subject to change as new versions are released. For more information on oncoKB, see [Chakravarty et al. 2017](https://ascopubs.org/doi/full/10.1200/PO.17.00011). 

## Installation

You can install the development version of oncokbR like so:

``` r
remotes::install_github('karissawhiting/oncokbR')
```
## Authentication

In order to use this packe, you will need to acquire a token and save it to your .Renviron file (or wherever you store credentials). You will need to register for an account on [OncoKB Precision Oncology Knowledge Base](https://www.oncokb.org/). Once your registration is approved, you will see a token under your [Account Settings](https://www.oncokb.org/account/settings). Save it in your .Renviron file. This will save the token as an environmental variable so you don’t have to hard code the secret key in your scripts.

*Tip: The following {usethis} function can easily find and open the .Renviron for you:*

```{r}
usethis::edit_r_environ()
```

Paste the token you were given (using the format below) in the .Renviron file and save the file changes. After saving you should restart your R session to ensure the token is saved and recognized.

```{r}
ONCOKB_TOKEN = 'YOUR_TOKEN'
```


## Annotate Data

### Annotate Mutations:

```{r}
library(oncokbR)
library(dplyr)
```

Annotate MAF data with tumor type indicated for annotations on oncogenicity and oncoKB treatment levels:

```{r }
blca_mutation <- oncokbR::blca_mutation %>%
  mutate(tumor_type = "BLCA")

annotated_tt <- annotate_mutations(mutations = blca_mutation[1:50,])

annotated_tt %>%
  select(oncogenic) %>% 
  table()

```


```{r}
annotated_tt %>%
  select(treatments_level ) %>% 
  table()
```

You can also annotated with no tumor type data for oncogenicity only: 

```{r }
blca_mutation <- oncokbR::blca_mutation

annotated_no_tt <- annotate_mutations(mutations = blca_mutation[1:50,])

annotated_no_tt %>%
  select(oncogenic) %>% table()
```


### Annotate CNA:

```{r}
blca_cna <- blca_cna %>%
  mutate(tumor_type = "BLCA")


annotated <- annotate_cna(blca_cna[1:10,])
table(annotated$oncogenic)

```

### Annotate Structural Variants:

```{r}

blca_sv <- blca_sv %>%
  mutate(tumor_type = "BLCA")


annotated <- annotate_sv(blca_sv[1:10,])
table(annotated$oncogenic)
```
