---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oncokbR

<!-- badges: start -->
<!-- badges: end -->

{oncokbR} allows you to annotate genomic data sets using MSK's [OncoKB Precision Oncology Knowledge Base](https://www.oncokb.org/) directly in R. The package wraps existing [OncoKB API endpoints](https://api.oncokb.org/oncokb-website/api) so R users can easily leverage the existing API to annotate data on mutations, copy number alterations and fusions.


This package is compatible with oncoKB data v3.16, but is subject to change as new versions are released. For more information on oncoKB, see [Chakravarty et al. 2017[(https://ascopubs.org/doi/full/10.1200/PO.17.00011). 

Gao et al. Sci. Signal. 2013
Cerami et al. Cancer Discov. 2012

## Installation

You can install the development version of oncokbR like so:

``` r
remotes::install_github('karissawhiting/oncokbR")
```

## Annotate Data

Annotate Mutations:

```{r}
library(oncokbR)
library(dplyr)

blca_mutation <- oncokbR::blca_mutation %>%
  mutate(tumor_type = "ACC")


annotated <- annotate_mutations(blca_mutation[1:20,])
table(annotated$oncogenic)
```

Annotate CNA:

```{r}
blca_cna <- blca_cna %>%
  mutate(tumor_type = "ACC")


annotated <- annotate_cna(blca_cna[1:10,])
table(annotated$oncogenic)
```
